Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-08 ms.tex
Make introduction about status quo and how Atomify improves on it

\section{Introduction}
Atomistic simulations insight blabla
Important blabla

Tools like, script editors, simulators, Ovito VMD defines the workflow.

>>>>

\section{Introduction}

Atomistic simulations are used in to materials modeling to provide insight into ...

Over the past decades, users of LAMMPS and other molecular dynamics simulators have
typically written scripts in a text editor and run the scripts by passing them to the simulator
on the command line.
The simulator in turn writes the results to disk and the user analyzes the results
by reading the files manually or passing them to other programs.
With the arrival of software like VMD,
it become easy to both visualize the trajectories and certain physical quantities.
VMD came with support both for reading the results from file or attaching to a
running process of supported simulators.
Later, modern visualization tools like Ovito has made both visualization and analysis more
accessible to new users.
In addition, the results can be loaded into common programming languages like MATLAB and Python
to produce publication-ready figures.

In combination, the text editors, the simulators, the visualization software, and the programming
languages like MATLAB and Python define the workflow of a typical researcher in computational
materials science.
While this is a powerful workflow in well-established simulations,
it is tedious for prototyping new ideas.
The workflow requires a fairly large amount of context switching,
moving from the text editor to the terminal to run the simulation,
waiting for the results, and then finally being able to study them using the analysis
and visualization tools.

Here, we present Atomify, a software that integrates script editing,
visualization and analysis into one tool.
Atomify has detailed knowledge about the inner workings of LAMMPS,
which makes it capable not only of visualizing the simulation results,
but also how the simulation is defined in terms of different groups and regions.
